---
title: "HouseProject"
author: "S18825"
date: "2023-09-26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```
```{r}
library(tinytex)
```

```{r}
col_type <- 'ddiilildf'
house_data <- read_csv("../Data/houseData.csv",col_types = col_type)
```
```{r}
head(house_data)
```
```{r}
summary(house_data)
```
```{r}
glimpse(house_data) # Find the no.of.rows and no.of.columns also find the summary
```
# DATA HANDLING
mutate() - Preprocess task
select()- get the subset of the data frame
filter()- filter the data
arrange() - how to arrange
summarize()- summarize the observation ; groupby()-
```{r}
select(house_data,salePrice,sqFeet)
```
```{r}
# sq feet more than 4500 ,here see that how many number of houses more than 4500
filter(house_data,sqFeet > 4500)
```

# Select the sale price ,square footage and year of construction of houses with a pool and built after 1980
```{r}
select_houses <- filter(house_data,pool== TRUE & year > 1980 )
select_houses
```

```{r}
select(select_houses,salePrice,sqFeet,year)
```
# Piping(%>%)
With out getting intermediate data set this pipe function used
get the clear understand #advantage
```{r}
house_data %>%
  filter(pool == TRUE & year > 1980) %>%
  select(salePrice,sqFeet,year)
```

# Arrange
Arrange the house built according to the sale price after 1980
Here Sales prices are asending order
```{r}
house_data %>%
  filter(year > 1980) %>%
  arrange(salePrice)
```
# desending order
```{r}
house_data %>%
  filter(year > 1980) %>%
  arrange(desc(salePrice))
```

# mutate
create and modify the variables
Calculate the number of bathroom per bed room

```{r}
house_data <- house_data %>%
  mutate(bathRmPerBed = baths / beds)
```


```{r}
head(house_data)
```
# Summarize - What we want require summary
Average of the price

```{r}
house_data %>%
  summarise(meanSalePrice = mean(salePrice))
```
# Average Price with swimming pool
```{r}
house_data %>%
  filter(pool == TRUE) %>%
  summarise(AvergeWithPoolPrice = mean(salePrice))
```
# Calulate average salesprice of withput swimming pool

```{r}
house_data %>%
  filter(pool == FALSE) %>%
  summarise(AvergeWithoutPoolPrice = mean(salePrice))
```

AvergeWithPoolPrice
<dbl>
352.1203	

AvergeWithoutPoolPrice
<dbl>
271.8674

# House with swimming ful is expensive than without swimming full

# Caluate average sale price for bed rooms
```{r}
head(house_data,2)

```

# Summarize with no of beds with pool 
```{r}
house_data %>%
  group_by(beds,pool) %>%
  summarise(count = n(),
            average_price = mean(salePrice),
            average_feet = mean(sqFeet))
```












